### 2017-09-30 TF-vldb2018/sec-tsim.tex

 Given pattern $P$, data graph $G$, and two positive integers $r, k$, the {\em top-$k$ team formation} problem, denoted as \teamF{(P, G, k)},
is to find a list $L_{k}$ of $k$ perfect subgraphs (\ie teams) with the top-$k$ largest density in $G$ for $P$, via team simulation.
\looseness=-1

@@

\ni(2) by minimizing the {\em sum of all-pair distances} of teams \cite{Kargar11},
which returns exactly the same team as (a) in this case, or

@@

We next introduce dynamic top-$k$ team formation.
%For convenience, the notations used are summarized in Table~\ref{tab-notation}.

@@

\stitle{Dynamic top-$k$ team formation}. Given pattern $P$, data graph $G$, two positive integers $r$, $k$, the list $L_{k}(P,G)$ of top-$k$ perfect subgraphs for $P$ in $G$,
a set of pattern updates $\Delta P$ and a set of data updates $\Delta G$,
the {\em dynamic top-k team formation} problem, denoted by \dynteamF{(P, G, k, L_{k}, \Delta P, \Delta G)},
is to find a list of $k$ perfect subgraphs with the top-$k$ largest density for $P\oplus\Delta P$ in $G\oplus\Delta G$, via team simulation.

It is worth mentioning that \dynteamF{} covers a broad range of dynamic situations,
\ie handling continuous separate and simultaneous pattern and data updates.
Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$, and
 $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.

>>>>

 Given pattern $P$, data graph $G$, and two positive integers $r$ and $k$, the {\em top-$k$ team formation} problem, denoted as \teamF{(P, G, k)},
is to find a list $L_{k}$ of $k$ perfect subgraphs (\ie teams) with the top-$k$ largest density in $G$ for $P$, via team simulation.
\looseness=-1

@@

\ni(2) by minimizing the {\em sum of all-pair distances} of teams \cite{Kargar11},
which returns exactly the same team as (1) in this case, or

@@

We now introduce dynamic top-$k$ team formation.
%For convenience, the notations used are summarized in Table~\ref{tab-notation}.

@@

\stitle{Dynamic top-$k$ team formation}. Given pattern $P$, data graph $G$, positive integers $r$ and $k$, the list $L_{k}(P,G)$ of top-$k$ perfect subgraphs for $P$ in $G$,
a set of pattern updates $\Delta P$ and a set of data updates $\Delta G$,
the {\em dynamic top-k team formation} problem, denoted by \dynteamF{(P, G, k, L_{k}, \Delta P, \Delta G)},
is to find a list of $k$ perfect subgraphs with the top-$k$ largest density for $P\oplus\Delta P$ in $G\oplus\Delta G$, via team simulation.

Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$, and
 $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.
 It is worth mentioning that \dynteamF{} covers a broad range of dynamic situations,
\ie handling continuous separate and simultaneous pattern and data updates.

### 2017-09-30 TF-vldb2018/sec-tsimAlg.tex

\subsection{Pattern Satisfiability}
Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
there exist pattern graphs match no data graphs via team simulation, due to the presence of capacity constraints on patterns. We illustrate this with an example.
%\looseness=-1

@@

\stitle{Handling radius varied balls}. \teamF{} is to find top-$k$ teams within balls $\ball{[v, t]}$, where $v \in V$ and $t \in [1,r]$.
%centered at each node in $G$ with radius $t$ varying from 1 to $r$.
However, it is very costly to construct all $r|V|$ balls, and to compute perfect subgraphs in all of them.
Indeed it is also not necessary, and it only needs to constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$
where $v \in V$ and radius is $r$, and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$, as shown below.

@@

Given a ball $\ball{[v,r]}$, we compute the density upper bound  $\density{\hat{G}_s}$,
where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
If the bound is larger than the density of the current $k$-th result, \ie there is a possibility the for the ball;
Otherwise, the ball is simply ignored to avoid redundant computations.

@@

\stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
It firstly checks whether $P$ is satisfiable (line 1).
If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the early termination condition holds (lines 3-6).
If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see full version~\cite{fullvldb18}),
an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the data incremental algorithms in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11).
%Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
%by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.

\stitle{Correctness \& complexity analyses}. The correctness of \grouprec is assured by the following.
%(1) There is a unique perfect subgraph in each ball of $G$.
(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as for simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
(2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
It takes $O(|P|^2)$ to check pattern satisfiability, $O(|V||P||G|)$ to compute team simulation, $O(r|V||V_{P}||E|)$ to incrementally compute matches in inner balls, and $O(|V||E|)$  to compute the density of the maximum core for $|V|$ balls.
Thus \grouprec is in $O(|P|^2+|V||P||G|+r|V||V_{P}||E|)$. However, actual time is much less due to early termination and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule
			\vspace{-3ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $k, r$.\\
				{\sl Output:\/} Top-$k$ densest teams.\\
				\sstab \bcc \hspace{1ex}\= \If $P$ is unsatisfiable \Then \Return $nil$;\\
				\icc \> $L_{k} := \emptyset$;\\
				\icc \> \For each ball $\ball{[v,r]}$ in $G$ \Do\\
				\icc \>\hspace{2ex}\= compute the maximum core $\ball{}_{C}$ of the ball $\ball{[v,r]}$;\\
				\icc \>\> \If 2*$\density{\ball{}_C} <$  the density of the $k$-th result in $L_{k}$ \Then\\
				\icc  \>\>\hspace{2ex}\= \Return $L_{k}[0:k-1]$;\\
				\icc \>\> $G_s$ := \rgraphsim$(P, \ball{[v,r]})$; \\
				\icc \>\> If $G_s$ satisfy capacity bounds on $P$ \Then Insert $G_s$ into $L_{k}$;\\
				\icc \>\> \For each ball $\ball{[v,t]}$ with $t\in[1,r-1]$ \Do\\
				\icc \>\>\hspace{2ex}\= $G'_s$ := \kw{incSim}$(G_s, P, \ball{[v,t]})$;\\
				\icc \>\>\> If $G'_s$ satisfy capacity bounds on $P$ \Then Insert $G'_s$ into $L_{k}$;\\
				%\icc \>\> \If $\density{G_s}>$ the density of the $k$-th result in $L_{k}$ \Then\\
				%\icc \>\> \If $\density{G_s}>$ the density of $kth$ result in $L_{k}$ and there exists\\
				%     \>\>\hspace{0.5ex}   no $G'_s$ in $L_{k}$ that is same with $G_{s}$ \Then\\
				%\icc \>\>\hspace{2ex}\= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$;\\
				\icc \>\, \Return $L_{k}[0:k-1]$.
			}

			\vspace{-4ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \grouprec}
	\label{alg-grouprec}
	\vspace{-4ex}
\end{figure}

>>>>

\subsection{Pattern Satisfiability}
Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
there exist patterns that cannot match any data graph via team simulation, due to the presence of capacity constraints on patterns. We illustrate this with an example.
%\looseness=-1

@@

\stitle{Handling radius varied balls}. \teamF{} is to find top-$k$ teams within balls $\ball{[v, t]}$, where $v \in V$ and $t \in [1,r]$.
%centered at each node in $G$ with radius $t$ varying from 1 to $r$.
However, it is very costly to construct all $r|V|$ balls, and to compute perfect subgraphs in all of them.
Indeed it is also not necessary, and it only needs to construct and compute the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$
where $v \in V$ and radius is $r$, and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$, as shown below.

@@

Given a ball $\ball{[v,r]}$, we compute the density upper bound  $\density{\hat{G}_s}$,
where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
If the bound is larger than the density of the current $k$-th result, \ie there is a possibility for the ball;
Otherwise, the ball is simply ignored to avoid redundant computations.

@@

\stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
It firstly checks whether $P$ is satisfiable (line 1).
If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the
density based ball filtering condition holds (lines 3-6).
If so, it skips the current ball, and moves to the next one;
otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see full version~\cite{fullvldb18}),
an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the data incremental algorithms in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11).
%Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
%by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.

\stitle{Correctness \& complexity analyses}. The correctness of \grouprec is assured by the following.
%(1) There is a unique perfect subgraph in each ball of $G$.
(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as graph simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
(2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
It takes $O(|P|^2)$ to check pattern satisfiability, $O(|V||P||G|)$ to compute team simulation, $O(r|V||V_{P}||E|)$ to incrementally compute matches in inner balls, and $O(|V||E|)$  to compute the density of the maximum core for $|V|$ balls.
Thus \grouprec is in $O(|P|^2+|V||P||G|+r|V||V_{P}||E|)$. However, actual time is much less due to density based ball filtering and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule
			\vspace{-3ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} $G(V$, $E)$, $P(V_P$, $E_P)$, and positive integers $r$ and $r$.\\
				{\sl Output:\/} Top-$k$ densest teams.\\
				\sstab \bcc \hspace{1ex}\= \If $P$ is unsatisfiable \Then \Return $nil$;\\
				\icc \> $L_{k} := \emptyset$;\\
				\icc \> \For each ball $\ball{[v,r]}$ in $G$ \Do\\
				\icc \>\hspace{2ex}\= compute the maximum core $\ball{}_{C}$ of the ball $\ball{[v,r]}$;\\
				\icc \>\> \If 2*$\density{\ball{}_C} <$  the density of the $k$-th result in $L_{k}$ \Then\\
				\icc  \>\>\hspace{2ex}\= \Continue;\\
				\icc \>\> $G_s$ := \rgraphsim$(P, \ball{[v,r]})$; \\
				\icc \>\> If $G_s$ satisfy capacity bounds on $P$ \Then Insert $G_s$ into $L_{k}$;\\
				\icc \>\> \For each ball $\ball{[v,t]}$ with $t\in[1,r-1]$ \Do\\
				\icc \>\>\hspace{2ex}\= $G'_s$ := \kw{incSim}$(G_s, P, \ball{[v,t]})$;\\
				\icc \>\>\> If $G'_s$ satisfy capacity bounds on $P$ \Then Insert $G'_s$ into $L_{k}$;\\
				%\icc \>\> \If $\density{G_s}>$ the density of the $k$-th result in $L_{k}$ \Then\\
				%\icc \>\> \If $\density{G_s}>$ the density of $kth$ result in $L_{k}$ and there exists\\
				%     \>\>\hspace{0.5ex}   no $G'_s$ in $L_{k}$ that is same with $G_{s}$ \Then\\
				%\icc \>\>\hspace{2ex}\= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$;\\
				\icc \>\, \Return $L_{k}[0:k-1]$.
			}

			\vspace{-4ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \grouprec}
	\label{alg-grouprec}
	\vspace{-3ex}
\end{figure}
